A Digital Library for Crowds on the Real-Time Social Web

### 2011-05-05 docs/csce_675/paper.tex
added api info

\subsection{HTTP JSON RESTful APIs}: This module provides client an interface to the digital library. The module exposes JSON APIs that the clients can use to browse and search the crowds archive.

>>>>

\subsection{HTTP JSON RESTful APIs}: This module provides client an interface to the digital library. The module exposes JSON APIs that the clients can use to browse and search the crowds archive. Here is a brief description of the more important methods:
\begin{description}
 \item[search/crowd] Find crowds sorted by relevance or time.
 \item[crowd/id] Retrieve all of the data for a crowd.
 \item[crowd/users] Retrieve a list of all the users in the crowd.
 \item[crowd/tweets] Retrieve a list of all the tweets in the crowd.
 \item[crowd/star] Mark a crowd as significant.
 \item[user/edges] Retrieve the friend and follower relationships for a given user.
\begin{description}
